Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-02-18 Manuscript/03-Simulation.Rmd
Initiate Var Select Section

In this section, we compare the performance of the proposed models to four alternative models: component selection and smoothing operator (COSSO) [@Zhang2006GAM], adaptive COSSO [@Storlie2011], generalized additive models with automatic smoothing [@Wood2011], SB-GAM [@Bai2021]\bg{}, linear lasso model and spikeSlabGAM [TODO: add citation here]}. COSSO is one of the earliest smoothing spline models that consider sparsity-smoothness penalty. Adaptive COSSO improved upon COSSO by using adaptive weight for penalties such that the penalty of each functional component are different for extra flexibility. Generalized additive models with automatic smoothing, hereafter \textit{mgcv}, is one of the most popular models for nonlinear effect interpolation and prediction. SB-GAM is the first spike-and-slab lasso GAM. We implement COSSO and adaptive COSSO with R package \texttt{cosso 2.1-1}, generalized additive models with automatic smoothing with R package \texttt{mgcv 1.8-31}, SB-GAM with R package \texttt{sparseGAM 1.0}. COSSO models and SB-GAM do not provide flexibility to define smoothing functions, and hence use the default choices. Both mgcv and proposed models allow customized smoothing functions and we choose the cubic regression spline. We controll the dimensionality of each smoothing function, 10 bases, for all different choices of smoothing functions. We use 5-fold CV with the default selection criteria to select the final model for COSSO models, SB-GAM and the proposed models. 20 default candidates of tuning parameters ($s_0$ in BHAM, $\lambda_0$ in SB-GAM) are examined for SB-GAM and the proposed models which allow user-specification of tuning candidates. All computation was conducted on a high-performance 64-bit Linux platform with 48 cores of 2.70GHz eight-core Intel Xeon E5-2680 processors and 24G of RAM per core and R 3.6.2 [@R].

@@

\subsection{Monte Carlo Simulation Study}
We follow the data generating process described in Bai [@Bai2021]. We first generate $n=500$ training data points with $p=4, 10, 50, 100, 200$ predictors respectively, where the predictors $X$ are simulated from a multivariate normal distribution $\text{MVN}_{n\times p}(0, I_{P})$. We then simulate the outcome $y$ from two distributions, Gaussian and binomial with the identity link and logit link $g(x) = \log(\frac{x}{1-x})$ respectively. The mean of each outcome were simulated via the following function
$$
\mathbb{E}(Y) = g^{-1}(5 \sin(2\pi x_1) - 4 \cos(2\pi x_2 -0.5) + 6(x_3-0.5) - 5(x_4^2 -0.3))
$$
for Gaussian and binomial outcomes.
<!-- and shrinked effects -->
<!-- $$ -->
<!-- \mathbb{E}(Y) = g^{-1}(\sin(2\pi x_1) - 2\cos(2\pi x_2 -0.5) + 0.4(x_3-0.5) - 2(x_4^2 -0.3)) -->
<!-- $$ -->
<!-- for  poisson outcomes.  -->
Gaussian outcomes requires specification of dispersion, where we set the dispersion parameter to be 1. In this data generating process, we have $x_1, x_2, x_3, x_4$ as the active covariates, while the rest covariates are inactive, i.e. $f_j(x_j) = 0$ for $j = 4, \dots, p$. Another set of independent sample of size $n_{test}=1000$, are created following the same data generating process, serving as the testing data. We generate 50 independent pairs of training and testing datasets to evaluate the prediction performance of the chosen models, where training datasets are used to fit the models and testing datasets used to calculate assessment measures. \bg{In addition, we considered the data generating process where the all the functional forms of the predictors are linear while keeping the rest of simulation parameters keep the same. These additional sets of simulations are designed to investigate the flexibility of the proposed model when non-linear assumptions are not met.}
<!-- The dimensional of the smoothing functions are controlled as k=10. Hence, the corresponding number of coefficient parameters to be estimated is 37, 82, 451 and 1801.  -->
<!-- We also run the simulation where the number of bases are increased to 25 deliberately. -->

To evaluate the predictive performance of the models, the statistics, $R^2$ for Gaussian model and AUC for binomial model calculated based on the testing dataset, are averaged <!--and deviance are calculated for Poisson model,--> across 50 simulations. \bg{To evaluate the variable selection performance of the models, we record the set of variables each model selects and calculate the averaged false discover rate (FDR), false negative rate(FNR), and Matthews correlation coefficient (MCC). For method that doesn't automatically achieve variable selection, we set alpha level at 0.05 for mgcv that relies on hypothesis testing for variable selection, and soft-threshold at 0.5 for spikeSlabGAM given the marginal inclusion probabilities. For the two methods, BHAM and spikeSlabGAM, that are capable of bi-level selection, we record the probability that the linear and nonlinear components of each predictors are selected in the models.}

\begin{center}
Table \ref{tab:gaus} here\\
Table \ref{tab:bin_auc} here\\
\end{center}
```{r, fig.height=8, eval = FALSE}
targets::tar_load(binom_plot)
binom_plot
```

```{r, fig.height=8, eval = FALSE}
targets::tar_load(gaussian_plot)
gaussian_plot
```

```{r, fig.height=8, eval = FALSE}
targets::tar_load(poisson_plot)
poisson_plot
```
\bg{\subsection{Simulation Results}}
\bg{\subsubsection{Prediction Performance}}
The predictive performances have a consistent pattern across the two distributions of outcomes. Across all the scenarios, COSSO and adaptive COSSO have the least favorable performance among the applicable methods examined (See Table \ref{tab:gaus} and \ref{tab:bin_auc}). To note, mgcv doesn't support high-dimensional analysis, i.e. the number of coefficients are greater than the sample size, and hence not evaluated when $p=100, 200$. mgcv predicts well when $p$ is small or moderate ($p = 4, 10$), and deteriorate when the number of predictors increase. Among the three fast-computing Bayesian hierarchical models, the proposed models, BHAM-IWLS and BHAM-CD predicts better than SB-GAM when the dimension of are moderate (p=4, 10, 50). Particularly, BHAM-IWLS performs as good as mgcv if not better. However, in high dimensional case where we mimic the situation the signals are extremely sparse, SB-GAM has better performance than the proposed method. However, the BHAM-CD has extreme computational advantage over SB-GAM (see Table \ref{tab:time_sim}) without sacrificing much of the prediction accuracy.

\bg{\subsubsection{Variable Selection Performance}}

\bg{\subsubsection{Bi-level Selection}
Among the methods of comparison, there are two methods is possible for bi-level selection, i.e. the proposed BHAM and spikeSlabGAM. Hence, in this section, we further investigate the bi-level selection of the proposed models. } 
<!-- %are calculated to assess out-of-sample estimation accuracy, -->

<!-- We also calculated the area under the curve (AUC) of the receiver operating characteristic curve for $y_{new}$. We will also visually display the estimated smooth function with the smooth function of truth to compare if the models can infer the smooth function correctly, despite the prediction accuracy. -->

<!-- The accuracy of variable selection is measured using Matthews correlation coefficient (MCC), -->
<!-- $$ -->
<!-- MCC = \frac{TP\times TN - FP \times FN}{\sqrt{(TP+FP)(TP+FN)(TN+FP)(TN+FN)}}, -->
<!-- $$ -->
<!-- where TP, TN, FP, and FN are true positives, true negatives, false positives, and false negatives, respectively. -->

<!-- ### Simulation Results -->

<!-- Overall, the proposed priors outperforms the state-of-the-art GAM model `mgcv` when the dimensionality is low, median, and high. The proposed priors predicts better than `mgcv` and infers better of the underlying smooth function. Most importantly, `mgcv` is infeasible in the high dimensional setting, i.e. when $p=50$ where the number of parameters are greater than the sample size.  -->

<!-- #### Prediction Performace -->

<!-- The prediction performance is tabulated in the table below for AUC and Supplementary tables for MSE and misclassification rate. In summary, the proposed Bayesian models outperforms the benchmark model `mgcv` regardless the choice of prior or fitting algorithm. The models with IRLS fitting algorithm give slightly better performance than the the model with cyclic coordinate descent algorithm. The advantage diminishes in the high dimensional setting (p=50). This is possible because the SS normal spline prior provides a more smooth solution, which would work well in a low to median dimension setting. However, in the high dimensional setting, there are not enough sparsity in the model, i.e. SS normal prior will provides a more complex model than necessary. This is confirmed with the visualization in the following section.  -->

```{r tab.id="sim_GAM_AUC", eval=F}
glm_spline_pred_dat <-readr::read_rds("Simulation_Result/predict_res.rds")

glm_spline_pred_dat$auc %>% 
        select(-c(n_train, n_test, "bglm_t", "bglm_de", "blasso")) %>% 
        flextable() %>% 
  set_caption(caption = "Averaged AUC of out-of-bag samples",
              autonum = run_autonum(seq_id = "tab", bkm="sim_GAM_AUC", pre_label = "Table "))
```

```{r  eval=F}
glm_spline_pred_dat <-readr::read_rds("Simulation_Result/predict_res.rds")

glm_spline_pred_dat$misclass %>% 
        select(-c(n_train, n_test, "bglm_t", "bglm_de", "blasso")) %>% 
        flextable() %>% 
  set_caption(caption = "Averaged misclassification rate of out-of-bag samples",
              autonum = run_autonum(seq_id = "tab", bkm="sim_GAM_Misclass", pre_label = "Table "))
```

```{r  eval=F}

glm_spline_pred_dat <-readr::read_rds("Simulation_Result/predict_res.rds")

glm_spline_pred_dat$mse %>% 
        select(-c(n_train, n_test, "bglm_t", "bglm_de", "blasso")) %>% 
        flextable() %>% 
  set_caption(caption = "Averaged mean squared area of out-of-bag samples",
              autonum = run_autonum(seq_id = "tab", bkm="sim_GAM_MSE", pre_label = "Table "))
```

>>>>

In this section, we compare the performance of the proposed models to four alternative models: component selection and smoothing operator (COSSO) [@Zhang2006GAM], adaptive COSSO [@Storlie2011], generalized additive models with automatic smoothing [@Wood2011], SB-GAM [@Bai2021]\bg{, linear lasso model and spikeSlabGAM [TODO: add citation here].[TODO: explain about linear lasso model and spikeSlabGAM model]}. COSSO is one of the earliest smoothing spline models that consider sparsity-smoothness penalty. Adaptive COSSO improved upon COSSO by using adaptive weight for penalties such that the penalty of each functional component are different for extra flexibility. Generalized additive models with automatic smoothing, hereafter \textit{mgcv}, is one of the most popular models for nonlinear effect interpolation and prediction. SB-GAM is the first spike-and-slab lasso GAM. We implement COSSO and adaptive COSSO with R package \texttt{cosso 2.1-1}, generalized additive models with automatic smoothing with R package \texttt{mgcv 1.8-31}, SB-GAM with R package \texttt{sparseGAM 1.0}. COSSO models and SB-GAM do not provide flexibility to define smoothing functions, and hence use the default choices. Both mgcv and proposed models allow customized smoothing functions and we choose the cubic regression spline. We controll the dimensionality of each smoothing function, 10 bases, for all different choices of smoothing functions. We use 5-fold CV with the default selection criteria to select the final model for COSSO models, SB-GAM and the proposed models. 20 default candidates of tuning parameters ($s_0$ in BHAM, $\lambda_0$ in SB-GAM) are examined for SB-GAM and the proposed models which allow user-specification of tuning candidates. All computation was conducted on a high-performance 64-bit Linux platform with 48 cores of 2.70GHz eight-core Intel Xeon E5-2680 processors and 24G of RAM per core and R 3.6.2 [@R].

@@

\subsection{Monte Carlo Simulation Study}
We follow the data generating process described in Bai [@Bai2021]. We first generate $n=500$ training data points with $p=4, 10, 50, 100, 200$ predictors respectively, where the predictors $X$ are simulated from a multivariate normal distribution $\text{MVN}_{n\times p}(0, I_{P})$. We then simulate the outcome $y$ from two distributions, Gaussian and binomial with the identity link and logit link $g(x) = \log(\frac{x}{1-x})$ respectively. The mean of each outcome were simulated via the following function
$$
\mathbb{E}(Y) = g^{-1}(5 \sin(2\pi x_1) - 4 \cos(2\pi x_2 -0.5) + 6(x_3-0.5) - 5(x_4^2 -0.3))
$$
for Gaussian and binomial outcomes. Gaussian outcomes requires specification of dispersion, where we set the dispersion parameter to be 1. In this data generating process, we have $x_1, x_2, x_3, x_4$ as the active covariates, while the rest covariates are inactive, i.e. $f_j(x_j) = 0$ for $j = 4, \dots, p$. Another set of independent sample of size $n_{test}=1000$, are created following the same data generating process, serving as the testing data. We generate 50 independent pairs of training and testing datasets to evaluate the prediction performance of the chosen models, where training datasets are used to fit the models and testing datasets used to calculate assessment measures. \bg{In addition, we considered the data generating process where the all the functional forms of the predictors are linear while keeping the rest of simulation parameters keep the same. These additional sets of simulations are designed to investigate the flexibility of the proposed model when non-linear assumptions are not met.}

To evaluate the predictive performance of the models, the statistics, $R^2$ for Gaussian model and AUC for binomial model calculated based on the testing dataset, are averaged <!--and deviance are calculated for Poisson model,--> across 50 simulations. \bg{To evaluate the variable selection performance of the models, we record the set of variables each model selects and calculate the averaged false discover rate (FDR), false negative rate(FNR), and Matthews correlation coefficient (MCC). For method that doesn't automatically achieve variable selection, we set alpha level at 0.05 for mgcv that relies on hypothesis testing for variable selection, and soft-threshold at 0.5 for spikeSlabGAM given the marginal inclusion probabilities. For the two methods, BHAM and spikeSlabGAM, that are capable of bi-level selection, we record the probability that the linear and nonlinear components of each predictors are selected in the models.
MCC = \frac{TP\times TN - FP \times FN}{\sqrt{(TP+FP)(TP+FN)(TN+FP)(TN+FN)}},
$$
where TP, TN, FP, and FN are true positives, true negatives, false positives, and false negatives, respectively.
$$
}
\bg{\subsection{Simulation Results}}
\bg{\subsubsection{Prediction Performance}}
The predictive performances have a consistent pattern across the two distributions of outcomes. Across all the scenarios, COSSO and adaptive COSSO have the least favorable performance among the applicable methods examined (See Table \ref{tab:gaus} and \ref{tab:bin_auc}). To note, mgcv doesn't support high-dimensional analysis, i.e. the number of coefficients are greater than the sample size, and hence not evaluated when $p=100, 200$. mgcv predicts well when $p$ is small or moderate ($p = 4, 10$), and deteriorate when the number of predictors increase. Among the three fast-computing Bayesian hierarchical models, the proposed models, BHAM-IWLS and BHAM-CD predicts better than SB-GAM when the dimension of are moderate (p=4, 10, 50). Particularly, BHAM-IWLS performs as good as mgcv if not better. However, in high dimensional case where we mimic the situation the signals are extremely sparse, SB-GAM has better performance than the proposed method. However, the BHAM-CD has extreme computational advantage over SB-GAM (see Table \ref{tab:time_sim}) without sacrificing much of the prediction accuracy.

\bg{

}

\bg{\subsubsection{Variable Selection Performance}
\begin{itemize}
\item If we use mcc as the measure, SBGAM has the best performance among all the method of comparison, followed by the proposed model BHAM. The pattern is consitent regardless of the type of outcomes. To note here, mgcv is not included in the performance table, as the mgcv isn't compatable with hign-dimensitonal data. Nevertheless, when the dimensionality is low, mgcv perfoms while for variable selection.
\item If we look at the precision of the variable selection, BHAM performs better than SBGAM model particularaly when the dimensionality increases. While the recall is lower than SBGAM. This translate to the selection of BHAM is more conservative that SBGAM, such that among the selected variables, many of them are signals, however, due to the conversative selection, there are few variables are selected.
\item We also want to high light that in the set of linear simulation, when the outcome is cgaussina, the proposed model performed extremely while. On the contrary the SBGAM is not so well.
\end{itemize}

}

\bg{\subsubsection{Bi-level Selection}
Among the methods of comparison, there are two methods is possible for bi-level selection, i.e. the proposed BHAM and spikeSlabGAM. Hence, in this section, we further investigate the bi-level selection of the proposed models. }

### 2022-02-18 Manuscript/SS_GAM.tex
Add bi-level selection section
Initiate Var Select Section

In this section, we compare the performance of the proposed models to
four alternative models: component selection and smoothing operator
(COSSO) \citep{Zhang2006GAM}, adaptive COSSO \citep{Storlie2011},
generalized additive models with automatic smoothing \citep{Wood2011},
SB-GAM \citep{Bai2021}\textcolor{red}{}, linear lasso model and
spikeSlabGAM {[}TODO: add citation here{]}\}. COSSO is one of the
earliest smoothing spline models that consider sparsity-smoothness
penalty. Adaptive COSSO improved upon COSSO by using adaptive weight for
penalties such that the penalty of each functional component are
different for extra flexibility. Generalized additive models with
automatic smoothing, hereafter \textit{mgcv}, is one of the most popular
models for nonlinear effect interpolation and prediction. SB-GAM is the
first spike-and-slab lasso GAM. We implement COSSO and adaptive COSSO
with R package \texttt{cosso 2.1-1}, generalized additive models with
automatic smoothing with R package \texttt{mgcv 1.8-31}, SB-GAM with R
package \texttt{sparseGAM 1.0}. COSSO models and SB-GAM do not provide
flexibility to define smoothing functions, and hence use the default
choices. Both mgcv and proposed models allow customized smoothing
functions and we choose the cubic regression spline. We controll the
dimensionality of each smoothing function, 10 bases, for all different
choices of smoothing functions. We use 5-fold CV with the default
selection criteria to select the final model for COSSO models, SB-GAM
and the proposed models. 20 default candidates of tuning parameters
(\(s_0\) in BHAM, \(\lambda_0\) in SB-GAM) are examined for SB-GAM and
the proposed models which allow user-specification of tuning candidates.
All computation was conducted on a high-performance 64-bit Linux
platform with 48 cores of 2.70GHz eight-core Intel Xeon E5-2680
processors and 24G of RAM per core and R 3.6.2 \citep{R}.

@@

@@

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ECB}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{225.2}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{228.2}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,506.4}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{34.4}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,540.7}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{WLM}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{483.1}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{7.6}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{490.7}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,116.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{32.7}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,148.7}}} \\

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Methods & Deviance & AUC & Brier & Misclass \\ 
  \hline
BHAM-CD & 455.69 & 0.74 & 0.16 & 0.21 \\ 
  SB-GAM & 1230.06 & 0.71 & 0.21 & 0.24 \\ 
   \hline
\end{tabular}
\caption{Prediction performance of BHAM fitted with Cooridnate Descent algorithm (BHAM-CD) and SB-GAM models for Emory Cardiovascular Biobank by 10-fold cross-validation, including deviance, area under the curve (AUC), Brier score, and misclassification error (Misclass) where class labels are defined using threshold = 0.5.} 
\label{tab:ECB_res}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Methods & Deviance & $R^2$ & MSE & MAE \\ 
  \hline
BHAM-CD & 665.63 & 0.07 & 0.94 & 0.75 \\ 
  SB-GAM & 666.83 & 0.03 & 0.98 & 0.77 \\ 
   \hline
\end{tabular}
\caption{Prediction performance of of BHAM fitted with Cooridnate Descent algorithm (BHAM-CD)  and SB-GAM models for Weight Loss Maintenance Cohort by 10-fold cross-validation, including deviance, $R^2$,  mean squared error (MSE), and mean absolute error (MAE).} 
\label{tab:WLM_res}
\end{table}

>>>>

In this section, we compare the performance of the proposed models to
four alternative models: component selection and smoothing operator
(COSSO) \citep{Zhang2006GAM}, adaptive COSSO \citep{Storlie2011},
generalized additive models with automatic smoothing \citep{Wood2011},
SB-GAM
\citep{Bai2021}\textcolor{red}{, linear lasso model and spikeSlabGAM [TODO: add citation here]}.
COSSO is one of the earliest smoothing spline models that consider
sparsity-smoothness penalty. Adaptive COSSO improved upon COSSO by using
adaptive weight for penalties such that the penalty of each functional
component are different for extra flexibility. Generalized additive
models with automatic smoothing, hereafter \textit{mgcv}, is one of the
most popular models for nonlinear effect interpolation and prediction.
SB-GAM is the first spike-and-slab lasso GAM. We implement COSSO and
adaptive COSSO with R package \texttt{cosso 2.1-1}, generalized additive
models with automatic smoothing with R package \texttt{mgcv 1.8-31},
SB-GAM with R package \texttt{sparseGAM 1.0}. COSSO models and SB-GAM do
not provide flexibility to define smoothing functions, and hence use the
default choices. Both mgcv and proposed models allow customized
smoothing functions and we choose the cubic regression spline. We
controll the dimensionality of each smoothing function, 10 bases, for
all different choices of smoothing functions. We use 5-fold CV with the
default selection criteria to select the final model for COSSO models,
SB-GAM and the proposed models. 20 default candidates of tuning
parameters (\(s_0\) in BHAM, \(\lambda_0\) in SB-GAM) are examined for
SB-GAM and the proposed models which allow user-specification of tuning
candidates. All computation was conducted on a high-performance 64-bit
Linux platform with 48 cores of 2.70GHz eight-core Intel Xeon E5-2680
processors and 24G of RAM per core and R 3.6.2 \citep{R}.

@@

\textcolor{red}{\subsubsection{Bi-level Selection}
Among the methods of comparison, there are two methods is possible for bi-level selection, i.e. the proposed BHAM and spikeSlabGAM. Hence, in this section, we further investigate the bi-level selection of the proposed models. }

@@

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ECB}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{100.8}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3.5}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{104.4}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{2,659.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{20.9}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{2,679.9}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{WLM}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{365.4}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{6.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{371.4}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,116.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{32.7}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,148.7}}} \\

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Methods & Deviance & AUC & Brier & Misclass \\ 
  \hline
BHAM-CD.1 & 510.99 & 0.61 & 0.19 & 0.24 \\ 
  BHAM-CD.2 & 510.99 & 0.61 & 0.19 & 0.24 \\ 
  SB-GAM & 636.56 & 0.56 & 0.22 & 0.30 \\ 
   \hline
\end{tabular}
\caption{Prediction performance of BHAM fitted with Cooridnate Descent algorithm (BHAM-CD) and SB-GAM models for Emory Cardiovascular Biobank by 10-fold cross-validation, including deviance, area under the curve (AUC), Brier score, and misclassification error (Misclass) where class labels are defined using threshold = 0.5.} 
\label{tab:ECB_res}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Methods & Deviance & $R^2$ & MSE & MAE \\ 
  \hline
BHAM-CD & 668.01 & 0.07 & 0.93 & 0.76 \\ 
  SB-GAM & 666.83 & 0.03 & 0.98 & 0.77 \\ 
   \hline
\end{tabular}
\caption{Prediction performance of of BHAM fitted with Cooridnate Descent algorithm (BHAM-CD)  and SB-GAM models for Weight Loss Maintenance Cohort by 10-fold cross-validation, including deviance, $R^2$,  mean squared error (MSE), and mean absolute error (MAE).} 
\label{tab:WLM_res}
\end{table}
